% load package if document contains at least one citation
\usepackage[maxbibnames=99,sorting=none,style=numeric,backend=biber]{biblatex}
% enable option to print bibliography as a numbered subsection
\defbibheading{bibsubsection}[\bibname]{%
  \subsection{#1}%
}
\addbibresource{refs.bib}


\begin{document}



%% Project-specific Preambles 
\settoggle{includelogo}{true}

\newcommand{\thesubject}{Informatik}
\newcommand{\thetopic}{MA Guidelines}
\newcommand{\theplace}{Winterthur}
\newcommand{\thelogo}{Logos/LeeLogo}
\newcommand{\logosize}{.5\textwidth}

\settoggle{oneauthor}{true}
\settoggle{twomainauthors}{false}
\def\mainauthors{
	Cyril Wendl/cyril.wendl@edu.zh.ch,
}

\lhead[ \leftmark ]{Informatik, Maturitätsarbeit}
\rhead[Informatik]{Cyril Wendl, \today, Winterthur}

\def\arrayB{"grinning-face","bar-chart","laptop","technologist","robot","woman-student","hundred-points"}
\maketitlepage{Maturitätsarbeit}{Report Guidelines}
\newpage
\tableofcontents\thispagestyle{empty}
\newpage
\setcounter{page}{1}

\section{Introduction}

This document serves as a \enquote{sidecar}, i.e., as an accompanying document to be used in addition to the official Vademecum for writing your \gls{MA}.

Your \gls{MA} should satisfy certain quality and formality criteria. This document aims at helping students in their writing process by outlining the most important aspects, without any claim to be comprehensive.

\section{Typesetting Tool}
In general, we highly recommend the use of \LaTeX{} for almost all \gls{MA} theses since it will take care of almost all formatting and style aspects (and needs) mentioned below. A tutorial on learning \LaTeX{} can be found here: \href{https://www.overleaf.com/learn/latex/Learn_LaTeX_in_30_minutes}{Overleaf tutorial}. For editing \LaTeX{} code, we highly recommend the \gls{IDE} \href{https://www.texstudio.org}{TeXstudio}.

We also recommend versioning your \LaTeX{} code on \url{https://github.com}. To learn more about why code versioning (version control) is important and how to do it, consult \href{https://docs.github.com/en/get-started/start-your-journey/about-github-and-git}{this tutorial}. For an easy and quick setup, consider installing \href{https://desktop.github.com/download/}{GitHub Desktop}, which contains an intuitive \gls{UI}.

Should you still prefer to use Microsoft Word or another (\href{https://de.wikipedia.org/wiki/WYSIWYG}{WYSIWYG}) typesetting tool, please stick to the following general rules:

\begin{itemize}
	\item \textbf{Justification}: Block justification with hyphenation
	\item \textbf{Page margins}: Roughly 3 cm on the left and right page margins
	\item \textbf{Font size}: 11--12 pt
	\item \textbf{Line distance}: make sure one page contains between 25--30 lines of text.
	\item \textbf{Titles and numbering}: Similar to this document, using \enquote{1 [Section Name 1], 2  [Section Name 2], 3  [Section Name 3]} for Sections and  \enquote{1.1 [Sub-Section Name 1]}, \enquote{1.2 [Sub-Section Name 2]}, \enquote{1.3 [Sub-Section Name 3]} for subtitles. Starting from the Appendix, number your Appendix Sections A, B, C etc. and number the appendix subsections A.1, A.2, A.3 etc. Again, if you're using \LaTeX, you wont need to worry about most of these aspects (see \cref{sec:latex} below for a list of LaTeX-related tips) as they are being taken care of automatically. This document, which itself has been generated using \LaTeX, can be used to see an example of such numbering.
	\item \textbf{Page numbering}: No page numbers on the title page and \gls{TOC}. Numbering starts at the first page of your \gls{MA} thesis containing actual contents.
\end{itemize}


\section{Length \& Structure}

The scope of the MA thesis should be defined by the topic. Typically, the number of pages should range anywhere between 10--20 written pages net, gross of further pages such as the title page, table of contents, references, table of figures, table of tables and further appendices.

Your thesis should have a logical and self-explanatory structure. Typically, your sections could be structured as follows:
\begin{itemize}
	\item \textbf{Title Page}: Title, possibly subtitle, author, supervisor, school, class name, \enquote{Maturitätsarbeit}, place and date
	\item \textbf{\acrlong{TOC}}: Overview of the sections and subsections of your thesis (in \LaTeX: just one line: \lstinline|\tableofcontents|).
	\item \textbf{Introduction} (numbering applies from here: 1(.1, .2), 2(.2,.3) etc.): Question / objective of your thesis, motivations, approach.
	\item \textbf{Methodology}: Overview of possible approaches to address your question and in-depth presentation of your approach, \textit{without}(!) presenting or discussing any results. If possible, also define a success metric (such as a number which you are trying to maximize, but can also be subjective) to assess the success of your thesis.
	\item \textbf{Results}: Present the results of your thesis
	\item \textbf{Discussion}: Assess and discuss the results.
	\item \textbf{Outlook}: What could or should be done to further improve your work if more time was available? Do not try to be too self-critical here but rather, this should reflect the fact that there is always more work to do (and in the case of scientific works, grants to obtain)
	\item \textbf{Conclusion}: A summary of the most important results and personal experiences during the process. Any further thoughts regarding the topic can also be inserted here.
	\item \textbf{Appendices} (numbered Appendix A(.1, .2), B(.1,.2), etc.): Statement of Independence (see Vademecum) as well as any appendix documents, such as questionnaires, code listings, further figures or tables, documents etc.
	\item \textbf{References}: Listing of all Materials, sources including online sources (in \LaTeX: just one line: \lstinline|\printbibliography|, have a look at the package \lstinline|biblatex|: \href{https://de.overleaf.com/learn/latex/Bibliography_management_with_biblatex}{Link}). Don't forget that you will have to compile your bibliography before it will show up in the document (In TeXStudio, this can be done using the key \keys{F8}).
	\item \textbf{Table of Figures} (in \LaTeX: just one line: \lstinline|\tableoffigures|).
	\item \textbf{Table of Table} (in \LaTeX: just one line: \lstinline|\tableoftables|)
	\item \textbf{Glossary}: List of abbreviations, if many abbreviations are used in the text  (in \LaTeX: just one line: \lstinline|\printglossaries|, have a look at the package \lstinline|glossaries|: \href{https://www.overleaf.com/learn/latex/Glossaries}{Link}). An example glossary is shown at the end of this document. Don't forget that you will have to compile your glossary before it will show up in the document (In TeXStudio, this can be done using the key \keys{F9}).

\end{itemize}


\section{Quotation Style}
You should clarify all contributions to your topic by citing any sources appropriately in your text. Again, citations are greatly facilitated if you use \LaTeX. We recommend reading through the following tutorial in depth: \href{https://de.overleaf.com/learn/latex/Bibliography_management_with_biblatex}{Link}. When you quote something in the middle of a sentence (always use quotation marks to do so), put the citation right after the quote, even if the sentence (in which the quote is embedded) has not been terminated yet. Conversely, in all other cases, meaning for sentences which are based on a source but do not contain literal quotes, add the citation in the end of the sentence, before the punctuation symbol.

\begin{tcolorbox}[title=Example]
	\begin{quotation}
		The recent breakthroughs in \gls{ML} and \gls{AI} in computing power have set new accuracy standards in many computer vision tasks, including, but not limited to, medical applications, autonomous driving and remote sensing \cite{Volpi2017DenseSL, kampffmeyer, Zhu2017DeepLI, Shelhamer2015FullyCN}. [...]
	\end{quotation}

\end{tcolorbox}

If you are citing an author literally use the \lstinline|\textcite| command instead of the \lstinline|\cite| command: While \lstinline|\cite| will only print the number of the relevant citation, \lstinline|\textcite| will also print the author name(s).

Typically, all citation meta-information, such as title, year of publication, author, etc. is contained in a \texttt{.bib} file (see \href{https://de.overleaf.com/learn/latex/Bibliography_management_with_biblatex}{tutorial} for more information). Citation information for a particular book or article can, many times, be obtained in \LaTeX{} format automatically from a database such as \url{https://www.semanticscholar.org}. You would also add any online links to this file, starting with a \lstinline|@online{...}| tag and you can quote it in the same way as other citations, such as here: \cite{Datenstrukturen}. For online sources, always add at least an author or institution name, the title of the webpage or video, the \gls{URL}, the  the date when you accessed the \gls{URL} last (field \lstinline|urldate| in the \texttt{.bib} file).

\section{Use of ChatGPT and other \acrshort{AI}-based Writing Tools}

The recent uprise of \gls{AI}-based writing tools, in particular \glspl{LLM} such as ChatGPT, enables a host of new possibilities for speeding up the writing process, especially for academic papers. However, as you may know, using such tools also comes with considerable limitations, as they often tend to give superficial, and sometimes even misleading and wrong answers. Hence, please consider the following recommendations on the use of ChatGPT and similar tools in your \gls{MA}:

\begin{enumerate}
	\item You can of course use ChatGPT as a tool for inspiration, for research, to help you reformulate your sentences in a more concise way, to give you feedback on your ideas and writing process, or to do other things more efficiently. However, be aware that ChatGPT's answers may be wrong and misleading – effectively creating more work for you than if you had done an old-fashioned internet search.
	\item If you use ChatGPT in your writing process (such as for reformulation of sentences or spell-check), please indicate this clearly in your \textit{Statement of Independence} (see Vademecum for further information on this section).
	\item There is currently no way to reliably prove that a sentence has been written by \glspl{LLM} such as ChatGPT -- however, we strongly discourage you to use ChatGPT to generate entire sentences, as this may also hamper your independent thinking and researching process, leading often to less creative and innovative solutions than if you had fully thought through the process yourself.
\end{enumerate}


\section{Writing style}
\subsection{Passive Style}
Wherever possible, use passive sentence styles and avoid the words \enquote{I} and \enquote{we}. This is standard in scientific writing, as it forces you into a more objective way of thinking.

\begin{tcolorbox}[title=Example]
	Instead of writing:
	\begin{quotation}
		After having searched the internet, I found that there were many options for doing \textit{xyz}...
	\end{quotation}
	You could write:
	\begin{quotation}
		In order to achieve \textit{xyz}, it seems that a variety of approaches are possible (insert citations!)
	\end{quotation}
\end{tcolorbox}

\subsection{Figures and Tables}
All figures and tables should add value to the text. This means that they should not only contain meaningful and added-value information but also a clear and informative caption stating what exactly can be seen in the figure or table. In addition, all figures and tables need to be referred to in the text explicitly (in \LaTeX{}, this is done using the tags \lstinline|\label{...}| and \lstinline|\ref{...}|). References to other sections should be done using the same approach. For more information, refer to Overleaf's \href{https://www.overleaf.com/learn/latex/Cross_referencing_sections%2C_equations_and_floats}{tutorial on cross-referencing}.

If you'd like to avoid having to type ``see \textit{Figure} \lstinline|\ref{...}|'' or ``see \textit{Table} \lstinline|\ref{...}|'' each time, you can use the \texttt{cleverref} package, using which you can just type ``see \lstinline|\cref{...}|''.

\subsection{Grammar Checks}
In order to check your grammar and spelling, please consider the following advice:
\begin{itemize}
	\item Have your \gls{MA} thesis proofread by at least 2--3 close acquaintences or family members who are proficient in English.
	\item Use online tools such as \url{https://www.grammarly.com/grammar-check} or ChatGPT (but don't write your entire thesis using the tool --– this greatly hampers creativity. Also, notice that there will be checks for plagiarism).
\end{itemize}

\newpage

\renewcommand{\thesubsection}{\Alph{subsection}}
\counterwithin{figure}{subsection}
\counterwithin{table}{subsection}
\pagebreak
\appendix
\section{Appendices}

\subsection{\LaTeX{} Related Advice}
\label{sec:latex}

\subsubsection{\LaTeX{} Related Tutorials}
Many good tutorials on \LaTeX{} can be found online. In particular, \href{https://www.google.com/search?client=safari&rls=en&q=overleaf+tutorial&ie=UTF-8&oe=UTF-8}{tutorials} provided by Overleaf can be a good starting point.

\subsubsection{Section Numbering for Appendix}
To change the section numbering style from numeric (numbers) to alphabetic (letters) use the following lines after the command \lstinline|\appendix|:

\begin{lstlisting}
% include the following line in the preamble: \usepackage{chngcntr}
\newpage
\renewcommand{\thesubsection}{\Alph{subsection}}
\counterwithin{figure}{subsection}
\counterwithin{table}{subsection}
\pagebreak  

\section{Appendices}

\subsection{Code Documentation}
% put contents here
\end{lstlisting}



\subsubsection{Bibliography Options}
For bibliographies in \LaTeX{}, we recommend studying the relevant \href{https://de.overleaf.com/learn/latex/Bibliography_management_with_biblatex}{Overleaf tutorial} and using the following parameters for citations:

\begin{lstlisting}
\usepackage[sorting=none,style=numeric,backend=biber]{biblatex}
\end{lstlisting}

\subsection{\LaTeX{} Code of this Document}
The following listing contains the \LaTeX{} code used for compiling this document (without the preamble, which would be too long to include). If you'd like to see the preamble as well or to get the \texttt{.tex} file shown in the listing below, feel free to reach out the authors of this document
\lstinputlisting[firstline=9]{Various/MA Thesis/MA Thesis Guidelines.tex}

\subsection{\LaTeX{} Code to Generate the Title Page of this Document}
The following listing contains the preamble and packages to generate the title page. You can of course also use a different or simpler title page, provided that all necessary information is shown on it. To get the \texttt{.tex} file shown in the listing below, feel free to reach out either to the authors of this document.

% \lstinputlisting[firstline=9]{Various/MA Thesis/titlepage_standalone.tex}

\newpage
\printbibliography

\newpage
\printglossaries
\end{document}